Fusion Moves for Correlation Clustering

### 2014-11-11 paper/inputs/fig_fusion.tex
made fusion figure smaller

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (1-2,3.5) -- (1-2,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
            {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x'}$}};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (1-2,3-3.5) -- (1-2,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x''}$}};

>>>>

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (1-1.5,3.5) -- (1-1.5,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
            {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x'}$}};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (1-1.5,3-3.5) -- (1-1.5,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x''}$}};
